Automated Network Packet Generation for Evaluation of Neural Networks in Intrusion Prevention Systems

### 2020-07-12 paper1/paper1.tex
Abstract, Intorduction and Conclusion added
Abstract, Intorduction and Conclusion added

\begin{abstract}
@Damir
\end{abstract}

@@

\section{Introduction}
@Damir [1p]

\newpage
test
\newpage

@@

\section{Conclusion}
@Damir [0.5p]

>>>>

\begin{abstract}
This Paper is a part of a project. It describes the part of automated network packet generation. The generated packets are used to evaluate neural networks in intrusion prevention systems. The challenges in this project include building the infrastructure and connecting the individual nodes in the network.
\end{abstract}

@@

\section{Introduction}
For a good, respectively successful detection of malicious network traffic using neural networks, the neural network has to be trained well. Therefore a large set of labelled network traffic is necessary. The more attack scenarios there were, the better the differentiation between attacks and normal traffic. Of course, not all possible scenarios can be dealt with here, which is why you have to concentrate on the attacks that occur most often in the real world. This subproject relates to the generation, labelling, distribution and recording of network data and packets. The network was deliberately kept simple and the different types of attacks were treated separately. The infrastructure was considered from scratch and implemented into a network simulation tool called \textit{GNS3}. To make the individual parts dynamic, the decision was made to use docker containers. This made it possible to evaluate the individual scenarios separately. The traffic was recorded using the \textit{tcpdump}, and the entire filtered traffic was saved in so-called pcap files. As far as the hardware is concerned, sufficient computing power was required, as well as sufficient storage space to be able to record the traffic.

@@

\section{Conclusion}
The result of this project can be used in the knowledge as well as in the structure. Due to the dynamic structure of the infrastructure, extensions can be added with little effort. During the implementation of the infrastructure, minor difficulties came up again and again, but these could usually be remedied with a relatively small change. Among other things, difficulties arose in the transfer of environment variables in the individual Docker containers. The other part of this project used this project as the basis, in which the recorded information and packages were evaluated. The successful evaluation showed that both the infrastructure and the individual nodes worked well.
